Legacy Data Confounds Modern Genomics Studies

### 2018-08-08 legacy.tex
Updated Figure 1 with regression values
Updated Figure 3 (minor edits to F1)

\author[1,2]{Luke Anderson-Trocm\'e}
\author[1,2]{Mathieu Bourgey}
\author[3]{Fumihiko Matsuda (and coauthors)}
\author[1,2]{Simon Gravel}

@@

To identify SNPs that are likely to reproduce poorly across cohorts (without having access to a second cohort), we performed a genome-wide association study (GWAS) in the JPT for SNPs that correlate strongly with low quality \ref{SFS}.
\luke{NEW:} 
Whereas the majority of GWAS use linear regression predicting a phenotype based on genotype, our method does the inverse.
We are looking for loci where the genotypes are predictable based on the data quality scores.
We were able to identify \todo{000} SNPs with $p < 10^{-8}$ and \todo{000} SNPs with $ p < 10^{-6}$.
While identifying putative low-quality SNPs to exclude, using a higher $p$-value threshold increases the stringency of the filtering (i.e., the traditional genome-wide significance threshold might not be a good guide for filtering).  
 %This GWAS included 104 Japanese individuals, 74 of which were sequenced in using the Genome Analyzer II while the rest were sequenced using the HiSeq 2000 of the 1kGP.
The variants that are associated to the quality of mapped bases have an enrichment in *AC${\rightarrow}$*CC mutations.

@@

	\subsection{Imputation}
The state of the art imputations servers use a combination of many databases including many that are not freely available.
For this reason, the details of the methods used to impute genomic data are not publicly available either.
In order to investigate the proportion of variants that we've identified as being associated to quality that are being imputed, we submitted the genotype data from the 1kGP and imputed it using the Michigan Imputation Server.
We found that \todo{~30\%} of the SNPs we identified as being associated with quality were imputed.

>>>>

\author[1,2]{Luke Anderson-Trocm\'e}
\author[1,2]{Mathieu Bourgey}
\author[1,2]{Rick Farouni}
\author[3]{Fumihiko Matsuda (and coauthors)}
\author[1,2]{Simon Gravel}

@@

To identify SNPs that are likely to reproduce poorly across cohorts (without having access to a second cohort), we performed a genome-wide association study (GWAS) in the JPT for SNPs that correlate strongly with low quality \ref{SFS}.
\luke{NEW:} 
Whereas the majority of GWAS use linear regression predicting a phenotype based on genotype, our method does the inverse.
We are looking for loci where the genotypes are predictable based on the data quality scores.
We were able to identify 587 SNPs with $p < 10^{-8}$ and 1034 SNPs with $ p < 10^{-6}$.
While identifying putative low-quality SNPs to exclude, using a higher $p$-value threshold increases the stringency of the filtering (i.e., the traditional genome-wide significance threshold might not be a good guide for filtering).  
 %This GWAS included 104 Japanese individuals, 74 of which were sequenced in using the Genome Analyzer II while the rest were sequenced using the HiSeq 2000 of the 1kGP.
The variants that are associated to the quality of mapped bases have an enrichment in *AC${\rightarrow}$*CC mutations.

@@

	\subsection{Imputation}
The state of the art imputations servers use a combination of many databases including many that are not freely available.
For this reason, the details of the methods used to impute genomic data are not publicly available either.
In order to investigate the proportion of variants that we've identified as being associated to quality that are being imputed, we submitted the genotype data from the 1kGP and imputed it using the Michigan Imputation Server.
We found that all of the SNPs we identified as being associated with quality were imputed.
